---
title: "MATH 216 Homework 5"
author: "Carter \"CartR\" Merenstein"
output: html_document
runtime: shiny
---


## Admistrative:

Please indicate

* Who you collaborated with: No one
* Roughly how much time you spent on this HW: 1.5 hr
* What gave you the most trouble: I still don't know how to upload to shiny server
* Any comments you have: 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Question 1:

* Pick three books from [Project Gutenberg](https://www.gutenberg.org/) and make
a "single-file" Shiny app based on file `App.R`
    + showing the corresponding wordcloud for a given book
    + that has "toggle" functionality to switch between the three books
* Note: Project Gutenberg tends to have older books whose copyright has expired.
* Install all necessary packages on your Middlebury Shiny server account
following the instructions given in Lec16 Shiny.
* Upload your app to the Middlebury Shiny server and replace the NHL link with
the link for your app [here](https://shiny.middlebury.edu:3838/cmerenstein/hw-5/), so that when you Knit the 
document a working hyperlink shows.

Hints:

* Get your code completely working for a non-Shiny app first, then build your
app slowly.
* If you get stuck, please ask for help sooner rather than later. I don't want 
people spinning their wheels on this HW this late in the semester.
* Consider using `if` and `else` statements to switch out which text to show the
wordcloud for. Note this isn't the only way to do this. Ex:


```{r, echo=FALSE}
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(stringr))
suppressPackageStartupMessages(library(tm))
suppressPackageStartupMessages(library(wordcloud))
suppressPackageStartupMessages(library(SnowballC))
suppressPackageStartupMessages(library(shiny))

filter_books <- function(book){
  trimmmed <- book %>%
  tolower() %>%
  removeNumbers() %>%
  removePunctuation() %>%
  removeWords(stopwords("english")) %>% 
  stripWhitespace()
  return(trimmmed)
}



Anne_of_Green_Gables <-
  readLines("pg45.txt", encoding="UTF-8") %>%
  as.character()

Anne_of_Avonlea <-
  readLines("pg47.txt", encoding="UTF-8") %>%
  as.character()

Anne_of_the_Island <-
  readLines("pg51.txt", encoding="UTF-8") %>%
  as.character()

#some sort of foreach would be helpful, I could put them in a vector

Anne_of_Green_Gables <- filter_books(Anne_of_Green_Gables)

Anne_of_Avonlea <- filter_books(Anne_of_Avonlea)

Anne_of_the_Island <- filter_books(Anne_of_the_Island)

GG <- VectorSource(Anne_of_Green_Gables) %>% 
  Corpus()

A <- VectorSource(Anne_of_Avonlea) %>% 
  Corpus()

tI <- VectorSource(Anne_of_the_Island) %>% 
  Corpus()

```

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("book", label = "Chose Book:",
              choices = c("Anne of Green Gables", "Anne of Avonlea", "Anne of the Island"), selected = "Anne of Green Gables")
  
)

renderPlot({
  if(input$book == "Anne of Green Gables") {
    wordcloud(GG, scale=c(5,0.5), max.words=25, random.order=FALSE,
          rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(8, "BuPu"))
} else if (input$book == "Anne of Avonlea") {
    wordcloud(A, scale=c(5,0.5), max.words=25, random.order=FALSE,
          rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(8, "BuPu"))
} else {
  wordcloud(tI, scale=c(5,0.5), max.words=25, random.order=FALSE,
          rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(8, "BuPu"))
}
})

#This is slow, because it draws the wordcloud again every time.
#I can't figure out how to save wordclouds, or I really just don't have the patience to.
```

